Title

### 2019-05-13 4_method.tex
better related work and related literature terminology

For an explanation of the terms used, see \cref{legend}.

@@

>>>>

\subsection{Terminology}
For an explanation of the terms used, see \cref{legend}.

@@

\subsubsection{In related literature}

``Because of its shape, the medial axis of a figure is also called the skeleton or the symmetric axis of the figure.
Associated with the medial axis is a radius function $R$, which defines for each point on the axis its distance to the boundary of the object.''
\cite{lee1982medial}

\cite{Moesen2011} provides a thorough overview of all MAT algorithms.
\cite{Moesen2011} calls $R$ the `feature radius': ``In every point $p \in P$, and thus also in points on the MA, thethe feature radius $\text{rad}(p)$ of $p$ can be defined as the Euclidean distance to the closest point on the boundary of $P$.''

\cite{kao1998optimal}
\begin{figure}[H]
\centering
\includegraphics[width=.9\columnwidth]{sources/method/distance_based_angles.pdf}
\caption{MAT explanation by Kao et al.}
\end{figure}
